Mixture Models for Single-Cell Assays with Application to Vaccine Studies: Supplementary Materials

### 2013-06-03 SupplementaryMaterialMIMOSA.tex
cut cut cut

>>>>

\noindent\textbf{Implementation Details for MCMC Algorithm}\\
We used the method of \cite{Raftery:1992vp} and Raftery \citep{Walter1996} to determine
the number of iterations, based on a short pilot run of the
sampler. For each dataset presented in the manuscript, we calculated that no more
than about 100,000 iterations with 50,000 burn-in iterations was sufficient to estimate standard posterior quantities. To leave some margin, we used 200,000 iterations after 50,000 burn-in iterations for each dataset explored here.
